---
output: html_document
---
My First MD R file
==================

This is my first R markdown file

here we are going to load some data
```{r}
library(datasets)
data(airquality)
summary(airquality)
```

lets make a plot

```{r}
pairs(airquality)
```

here is a regression model

```{r}
library(stats)
fit<-lm(Ozone~Wind+Solar.R+Temp,data=airquality)
summary(fit)
```

* first
* second
* third

Add some inline compuations by using echo=FALSE within the {}
```{r computetime,echo=FALSE}
time <- format(Sys.time(),"%a %b %d %X %Y")
rand <-rnorm(1)
```
The current time is `r time`. My favorite number is `r rand`.

###Some Figures!

simulate some data 
```{r}
x<-rnorm(100)
y<-x+rnorm(100,sd=0.5)
```
Scatter plot of the data 
```{r}
par(mar = c(5,4,1,1),las=1)
plot(x,y,main = "Simulated me")
```

with the height adjusted with fig.height=4 in the {}
```{r fig.height=4}
par(mar = c(5,4,1,1),las=1)
plot(x,y,main = "Simulated me")
```

###A nice table
```{r showtable,results='asis'}
library(xtable)
xt<-xtable(summary(fit))
print(xt,type="html")
```

Set global options within an R {} opts_chunk$set(echo=FALSE, results="hide")
Use cache=TRUE on chunks if running code multiple times and there are some chunks that take a long time to run
